---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bodleianlibraries

The goal of **bodleianlibraries** is to provide a convenient way of searching the Oxford Bodleian Libraries catalogue (SOLO) directly from the R console. When working on small screens in particular, switching from the R console to the browser window, opening a new tab, navigating to the desired website and finally searching for the search terms requires around 3-6 clicks. As one is working mainly in the R console, it is more convenient to start typing the search terms right away, without having to go through the process mentioned above. For example, `bodleian("a book that I am looking for")` will open the SOLO search for "a book that I am lookin for" in a new browser tab automatically.

#### Browser

To use a browser other than the default on your computer use `options(browser = "path to browser")`. For example, on macOS `options(browser = "/usr/bin/open -a '/Applications/Safari.app'")` or Windows `options(browser = "C:\\Program Files (x86)\\Internet Explorer\\iexplore.exe")`. To check which browser is set as the default use `getOption("browser")`.


## Installation

You can install bodleianlibraries from GitHub:
```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("fschaff/bodleianlibraries")
```

Please report issues or requests for additional functionality to https://github.com/fschaff/bodleianlibraries/issues.

## Example

```{r example}
library(bodleianlibraries)

# Try:

bodleian("a book that I am looking for")

```
